Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
a0 is active not public in fig 3
Abstract

The hardware stack interacts with a large number of language features,
some of which are typically excluded from discussions of stack
safety. Our properties go further than previous proposals in
supporting caller- and callee-saved registers, arguments passed on the
stack, \ifexceptions tail-call elimination, and exceptions.  \else and
tail-call elimination. \fi They are modular by design, in order to be
further extensible to other features.

>>>>

The hardware stack interacts with a large number of language features,
some of which are typically excluded from discussions of stack
safety. Our properties go further than previous proposals,
supporting caller- and callee-saved registers, arguments passed on the
stack, \ifexceptions tail-call elimination, and exceptions.  \else and
tail-call elimination. \fi They are modular by design so that they
can be further extended to other features.
